# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
data <- read.csv("activity.csv", colClasses=c("numeric", "Date", "numeric"))
```

## What is mean total number of steps taken per day?

Histogram of the total number of steps taken each day
```{r fig.width=15, fig.height=6}
stepsEachDay<-aggregate(data$steps, by=list(data$date), FUN=sum, na.rm=TRUE)
par(mar=c(8,2,2,2))
bp<-barplot(stepsEachDay$x, las=3)
axis(1,at=bp,labels=stepsEachDay$Group.1,las=3)
```

Mean and median total number of steps taken per day
```{r}
mean(stepsEachDay$x)
median(stepsEachDay$x)
```

## What is the average daily activity pattern?

```{r fig.width=7, fig.height=6}
stepsEach5Mins<-aggregate(data$steps, by=list(data$interval), FUN=mean, na.rm=TRUE)
plot(stepsEach5Mins$Group.1, stepsEach5Mins$x, type="l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
stepsEach5Mins[which(stepsEach5Mins$x==max(stepsEach5Mins$x)),]$Group.1
```

## Imputing missing values

```{r fig.width=15, fig.height=6}
library(plyr)
impute.steps <- function(x) replace(x, is.na(x), ceiling(mean(x, na.rm = TRUE)))
data<-ddply(data, ~interval, transform, steps = impute.steps(steps))
stepsEachDay<-aggregate(data$steps, by=list(data$date), FUN=sum, na.rm=TRUE)
par(mar=c(8,2,2,2))
bp<-barplot(stepsEachDay$x, las=3)
axis(1,at=bp,labels=stepsEachDay$Group.1,las=3)
mean(stepsEachDay$x)
median(stepsEachDay$x)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(lattice)
data$Day <- weekdays(data$date)
data$dayType[data$Day=="Sunday"]<-"weekend"
data$dayType[data$Day=="Saturday"]<-"weekend"
data$dayType[is.na(data$dayType)]<-"weekday"
data$dayType<-as.factor(data$dayType)
stepsEach5Mins<-aggregate(data$steps, by=list(data$interval, data$dayType), FUN=mean, na.rm=TRUE)
xyplot(stepsEach5Mins$x~stepsEach5Mins$Group.1|stepsEach5Mins$Group.2, layout=c(1,2), type="l", xlab="Interval", ylab="Number of steps")
```